---
title: "Untitled"
author: "Isabella Kaczmrczyk"
date: "19/03/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

library(R.matlab)
temp <- readMat("1MV_ERP_data_spvs90_15subjects.mat")



```{r}
library(ggpubr)
library(magrittr)
library(dplyr)
library(ggplot2)
library(ggsignif)
library(cowplot)

setwd("/omega/raw_TMS_EEG_Data/CorrelationData")


ntbl <- list.files(pattern = "*.csv") %>% 
    map_df(~read_csv(.,col_names = FALSE)%>%
            rename(TEP=X1, MEP=X2)%>%
            mutate(.,subject = c(1:15))  %>%
            mutate(.,con = "sp") %>%
            mutate(.,wave = "p60"))



# USE ME 
ldcor <- function(x,y,z)  # x = fiule name, y = sp or sici, z = wAVW
{
            temp <- read_csv(x,col_names = FALSE)
            temp <- rename(temp, TEP=X1, MEP=X2)
            temp <- mutate(temp,subject = c(1:15))
            temp <- mutate(temp,con = y)
            temp <- mutate(temp,wave = z)
            temp <- as.data.frame(temp)
            #temp <- as.data.frame(temp)

}


tbl <- bind_rows(ldcor("sp_n15.csv","sp","n15"),ldcor("sp_p30.csv","sp","p30"))
tbl <- bind_rows(tbl,ldcor("sp_n45.csv","sp","n45"))
tbl <- bind_rows(tbl,ldcor("sp_p60.csv","sp","p60"))
tbl <- bind_rows(tbl,ldcor("sp_n100.csv","sp","n100"))
tbl <- bind_rows(tbl,ldcor("sp_p180.csv","sp","p180"))

tbl <- bind_rows(tbl,ldcor("sp_n15.csv","sp","n15"))
tbl <- bind_rows(tbl,ldcor("sp_p30.csv","sp","p30"))
tbl <- bind_rows(tbl,ldcor("sp_n45.csv","sp","n45"))
tbl <- bind_rows(tbl,ldcor("sp_p60.csv","sp","p60"))
tbl <- bind_rows(tbl,ldcor("sp_n100.csv","sp","n100"))
tbl <- bind_rows(tbl,ldcor("sp_p180.csv","sp","p180"))


tbl <- bind_rows(tbl,ntbl)

library(corrr)

tbl2 <- x %>% 
  filter(con=="sp",wave=="N100") %>%
  select(TEP, MEP) %>%
  correlate(method = c( "spearman"), quiet = TRUE,diagonal = 1) %>%
  shave() %>%
  rplot()

mutate(x,subject = c(1:15),condition=condition)

mutate(x,con = "con")
library(reshape2)
mysici70<- melt(mysici70, id.vars=c("subjects"))

mysici80 <- read_csv("/omega/raw_TMS_EEG_Data/sici_80_peaks.csv")
mysici80 <- as.data.frame(mysici80)
mysici80 <- t(mysici80)
mysici80 <- as.data.frame(mysici80)
mysici80 <- rename(mysici80, c("V1"="N15", "V2"="P30", "V3"="N45","V4"="P60","V5"="N100" ))
rownames(mysici80) <- c(1:15)
mysici80$subjects <- c(1:15)
library(reshape2)
mysici80 <- melt(mysici80, id.vars=c("subjects"))

mysici90 <- read_csv("/omega/raw_TMS_EEG_Data/sici_90_peaks.csv")
mysici90 <- as.data.frame(mysici90)
mysici90 <- t(mysici90)
mysici90 <- as.data.frame(mysici90)
mysici90 <- rename(mysici90, c("V1"="N15", "V2"="P30", "V3"="N45","V4"="P60","V5"="N100" ))
rownames(mysici90) <- c(1:15)
mysici90$subjects <- c(1:15)
library(reshape2)
mysici90 <- melt(mysici90, id.vars=c("subjects"))


mysp <- read_csv("/omega/raw_TMS_EEG_Data/sp_peaks.csv")
mysp <- as.data.frame(mysp)
mysp <- t(mysp)
mysp <- as.data.frame(mysp)
mysp <- rename(mysp, c("V1"="N15", "V2"="P30", "V3"="N45","V4"="P60","V5"="N100" ))
rownames(mysp) <- c(1:15)
mysp$subjects <- c(1:15)
library(reshape2)
mysp <- melt(mysp, id.vars=c("subjects"))


mydata <- bind_rows(mysp, mysici70, mysici80, mysici90)
```


```{r}
setwd("/omega/raw_TMS_EEG_Data/")
myfiles <- list.files() # grabs the list 
dframes <- lapply(myfiles, myimport)  # importS THEN ALL
```


```{r}

# TMS SICI
fig1a <- data.frame(dframes[1])
fig1a$Condition <- factor(fig1a$Condition, levels = c("spTMS", "SICI70", "SICI80", "SICI90"))
my_1acomparisons <- list( c("spTMS", "SICI70"), c("spTMS", "SICI80"), c("spTMS", "SICI90") )

#TEP
fig1b <- data.frame(dframes[2])
fig1b$Peak <- factor(fig1b$Peak, levels = c("N15", "P30", "N45", "P60"))
fig1b$Condition <- factor(fig1b$Condition, levels = c("SP", "SICI_70", "SICI_80", "SICI_90"))
my_1bcomparisons <- list( c("SP", "SICI_70"), c("SP", "SICI_80"), c("SP", "SICI_90") )


#TEP
fig1c <- data.frame(dframes[3])
fig1c$Peak <- factor(fig1c$Peak, levels = c("N15", "P30", "N45", "P60"))
fig1c$Condition <- factor(fig1c$Condition, levels = c("SICI_70", "SICI_80", "SICI_90"))

# TMS SICI
fig1d <- data.frame(dframes[4])
fig1d$Condition <- factor(fig1d$Condition, levels = c("spTMS", "SICI70"))

# TMS SICI
fig1e <- data.frame(dframes[5])
fig1e$Condition <- factor(fig1e$Condition, levels = c("spTMS", "SICI80"))

# TMS SICI
fig1f <- data.frame(dframes[6])
fig1f$Condition <- factor(fig1f$Condition, levels = c("spTMS", "SICI90"))

# TMS SICI
fig2a <- data.frame(dframes[7])
fig2a$Condition <- factor(fig2a$Condition, levels = c("spTMS", "High ", "Medium", "Low"))
my_2acomparisons <- list( c("spTMS", "High "), c("spTMS", "Medium"), c("spTMS", "Low") )

#TEP
fig2b <- data.frame(dframes[8])
fig2b$Peak <- factor(fig2b$Peak, levels = c("N15", "P30", "N45", "P60"))
fig2b$Condition <- factor(fig2b$Condition, levels = c("spTMS", "High", "Medium", "Low"))
my_2bcomparisons <- list( c("spTMS", "High"), c("spTMS", "Medium"), c("spTMS", "Low") )
#TEP
fig2c <- data.frame(dframes[9])
fig2c$Peak <- factor(fig2c$Peak, levels = c("N15", "P30", "N45", "P60"))
fig2c$Condition <- factor(fig2c$Condition, levels = c("High", "Medium", "Low"))
my_comparisons <- list( c("spTMS", "High"), c("spTMS", "Medium"), c("spTMS", "Low") )

#SICI
fig2d <- data.frame(dframes[10])
fig2d$Condition <- factor(fig2d$Condition, levels = c("spTMS", "High"))

#SICI
fig2e <- data.frame(dframes[11])
fig2e$Condition <- factor(fig2e$Condition, levels = c("spTMS", "Medium"))

#SICI
fig2f <- data.frame(dframes[12])
fig2f$Condition <- factor(fig2f$Condition, levels = c("spTMS", "Low"))


#max(fig1a[SICI70]$MEP, na.rm = TRUE)


```


```{r}
library(ggpubr)
 
  ggviolin(data = fig1a,x = "Condition", y = "MEP",fill = "Condition",
   palette = c("#00AFBB", "#E7B800","#E7B800", "#FC4E07")) +
  geom_dotplot(binaxis="y",stackdir="center",binwidth=0.06,alpha = 0.35)+
  stat_summary(fun.data = "mean_cl_boot", colour = "black", size = 0.5,fill='black')+
  theme_classic() +
  stat_compare_means(comparisons = my_1acomparisons, label.y = c(1.9, 2.05, 2.2),hide.ns = TRUE,label = "p.signif") +
  theme(text = element_text(size=14), axis.text.x=element_blank(),legend.position = "none") +
  labs(x = "Condition",y= "Motor Evoked Potential (mV)") 

plot1a <- ggplot(data = fig1a, aes(x = Condition, y = MEP)) +
  geom_violin( aes(fill = factor(Condition))) +
  geom_dotplot(binaxis="y",stackdir="center",binwidth=0.04,alpha = 0.35)+
  stat_summary(fun.data = "mean_cl_boot", colour = "black", size = 0.5,fill='black')+
  theme_classic() +
  stat_compare_means(comparisons = my_1acomparisons, label.y = c(1.9, 2.05, 2.2),hide.ns = TRUE,label = "p.signif") +
  theme(text = element_text(size=14), axis.text.x=element_blank(),legend.position = "none") +
  labs(x = "Condition",y= "Motor Evoked Potential (mV)") 

colour =c("#999999", "#999999", "#56B4E9","#999999")

plot1b <- ggplot(data = fig1b, aes(x = Condition, y = TEP), xlab ="")    +
  facet_wrap(~ Peak, ncol=4) +
  geom_violin(aes(fill = factor(Condition))) +
  scale_fill_brewer(palette="Pastel1") + 
  geom_dotplot(binaxis="y",stackdir="center",binwidth=0.4,alpha = 0.35) +
   stat_summary(fun.data = "mean_cl_boot", colour = "black", size = 0.5,fill='black') +
  theme_classic() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),legend.title = element_blank()) + 
  stat_compare_means(comparisons = my_1bcomparisons, label.y = c(15, 16.5, 18))

plot1c <- ggplot(data = fig1c, aes(x = Condition, y = TEP_change), xlab ="")  +
  facet_wrap(~ Peak, ncol = 4) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), aes(fill = factor(Condition))) + scale_fill_brewer(palette="Pastel1") + 
  geom_dotplot(binaxis="y",stackdir="center",binwidth=0.04, color="white") + stat_summary(fun.data=data_summary, geom="crossbar", width=0.1 ) +  
  theme_classic() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
  theme(legend.position="bottom", legend.title = element_blank())

plot1d <- ggplot(data = fig1d, aes(x = Time, y = TEP, group = Condition))+
  geom_errorbar(aes(ymin=TEP-SE, ymax=TEP+SE, group = Condition, color = Condition)) +
  geom_line() +
  xlab("Time /ms") +
  ylab("TEP Amplitude /µV") +
  scale_color_brewer(palette="Pastel1") +
  theme_classic() +
  theme(legend.position="bottom", legend.title = element_blank())

plot1e <- ggplot(data = fig1e, aes(x = Time, y = TEP, group = Condition))+
  geom_errorbar(aes(ymin=TEP-SE, ymax=TEP+SE, group = Condition, color = Condition)) +
  geom_line() +
  xlab("Time /ms") +
  ylab("TEP Amplitude /µV") +
  scale_color_brewer(palette="Pastel1") +
  theme_classic() +
  theme(legend.position="bottom", legend.title = element_blank())

plot1f <- ggplot(data = fig1f, aes(x = Time, y = TEP, group = Condition))+
  geom_errorbar(aes(ymin=TEP-SE, ymax=TEP+SE, group = Condition, color = Condition)) +
  geom_line() +
  xlab("Time /ms") +
  ylab("TEP Amplitude /µV") +
  scale_color_brewer(palette="Pastel1") +
  theme_classic() +
  theme(legend.position="bottom", legend.title = element_blank())
```


```{r}

theme_set(theme_cowplot(font_size=8)) # reduce default font size
plot_grid(plot1a, plot1b, NULL,  plot1c, plot1d, plot1e, plot1f, labels = c('A', 'B', 'C',NULL, 'D'), align = "h", ncol = 2,nrow = 3)

plot_grid(plot1a, plot1b, labels = c('A', 'B'), align = "h", ncol = 2)
plot_grid(plot1a, plot1b, labels = c('A', 'B'), align = "h", ncol = 2)
ggsave("temp.png")

```




```{r}

plot2a <- ggplot(data = fig2a, aes(x = Condition, y = MEP)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75),aes(fill = factor(Condition))) + scale_fill_brewer(palette="Pastel1") + 
  geom_dotplot(binaxis="y",stackdir="center",binwidth=0.04, color="white") + stat_summary(fun.data=data_summary, geom="crossbar", width=0.1 ) +
  theme_classic() + stat_compare_means(comparisons = my_2acomparisons, label.y = c(1.5, 1.6, 1.7)) +
  theme(legend.position="bottom", legend.title = element_blank())

plot2b <- ggplot(data = fig2b, aes(x = Condition, y = TEP), xlab ="")    +
  facet_wrap(~ Peak, ncol = 4) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), aes(fill = factor(Condition))) + scale_fill_brewer(palette="Pastel1") + 
  geom_dotplot(binaxis="y",stackdir="center",binwidth=0.04, color="white") + stat_summary(fun.data=data_summary, geom="crossbar", width=0.1 ) +  
  theme_classic() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
  stat_compare_means(comparisons = my_2bcomparisons, label.y = c(13, 14, 15)) +
  theme(legend.position="bottom", legend.title = element_blank())

plot2c <- ggplot(data = fig2c, aes(x = Condition, y = TEP), xlab ="")  +
  facet_wrap(~ Peak, ncol = 4) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), aes(fill = factor(Condition))) + scale_fill_brewer(palette="Pastel1") + 
  geom_dotplot(binaxis="y",stackdir="center",binwidth=0.04, color="white") + stat_summary(fun.data=data_summary, geom="crossbar", width=0.1 ) +  
  theme_classic() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) + 
  theme(legend.position="bottom", legend.title = element_blank())

plot2d <- ggplot(data = fig2d, aes(x = Time, y = TEP, group = Condition))+
  geom_errorbar(aes(ymin=TEP-SE, ymax=TEP+SE, group = Condition, color = Condition)) +
  geom_line() +
  xlab("Time /ms") +
  ylab("TEP Amplitude /µV") +
  scale_color_brewer(palette="Pastel1") +
  theme_classic() +
  theme(legend.position="bottom", legend.title = element_blank())

plot2e <- ggplot(data = fig2e, aes(x = Time, y = TEP, group = Condition))+
  geom_errorbar(aes(ymin=TEP-SE, ymax=TEP+SE, group = Condition, color = Condition)) +
  geom_line() +
  xlab("Time /ms") +
  ylab("TEP Amplitude /µV") +
  scale_color_brewer(palette="Pastel1") +
  theme_classic() +
  theme(legend.position="bottom", legend.title = element_blank())

plot2f <- ggplot(data = fig2f, aes(x = Time, y = TEP, group = Condition))+
  geom_errorbar(aes(ymin=TEP-SE, ymax=TEP+SE, group = Condition, color = Condition)) +
  geom_line() +
  xlab("Time /ms") +
  ylab("TEP Amplitude /µV") +
  scale_color_brewer(palette="Pastel1") +
  theme_classic() +
  theme(legend.position="bottom", legend.title = element_blank())
```




















